\textsf{Are large language models superhuman chemists?}

### 2024-10-31 src/tex/appendix.tex
prepare for latex
Former-commit-id: c6a611cc108b38d941430242ce74a65e47dc7aa3

\begin{itemize}
    \item \textbf{Originality:} Questions should not be readily findable online or in other easily accessible sources (example \url{https://github.com/lamalab-org/chem-bench/pull/392#discussion_r1694299474})
    \item \textbf{Ambiguity:} Questions with unclear wording or multiple interpretations (example \url{https://github.com/lamalab-org/chem-bench/pull/420#discussion_r1698147159} )
    \item \textbf{Factual or heuristic Errors: }Questions containing factual inaccuracies or misconceptions are not included (example \url{https://github.com/lamalab-org/chem-bench/pull/389#discussion_r1686187301})
    \item \textbf{Clarity and Difficulty: } They should pose a challenge and encourage exploration within the chemical domain (example \url{https://github.com/lamalab-org/chem-bench/pull/391#discussion_r1679276714})
    \item \textbf{Out of Scope:} Questions outside the realm of chemistry are rejected.
    \item \textbf{Contribution to Dataset Diversity: }Questions should cover a wide range of chemical concepts and sub-disciplines. They should add value by expanding the breadth of the dataset. That is, questions already multiple (>10) times in the corpus in a similar form are rejected.
\end{itemize}

@@

In addition to the manual review, we also performed automated checks to ensure the quality of the questions. The schemas, Latex templating, and other formatting aspects are checked automatically using GitHub Actions.

>>>>

\begin{itemize}
    \item \textit{Originality:} Questions should not be readily findable online or in other easily accessible sources (example \url{https://github.com/lamalab-org/chem-bench/pull/392#discussion_r1694299474})
    \item \textit{Ambiguity:} Questions with unclear wording or multiple interpretations (example \url{https://github.com/lamalab-org/chem-bench/pull/420#discussion_r1698147159} )
    \item \textit{Factual or heuristic Errors: }Questions containing factual inaccuracies or misconceptions are not included (example \url{https://github.com/lamalab-org/chem-bench/pull/389#discussion_r1686187301})
    \item \textit{Clarity and Difficulty: } They should pose a challenge and encourage exploration within the chemical domain (example \url{https://github.com/lamalab-org/chem-bench/pull/391#discussion_r1679276714})
    \item \textit{Out of Scope:} Questions outside the realm of chemistry are rejected.
    \item \textit{Contribution to Dataset Diversity: }Questions should cover a wide range of chemical concepts and sub-disciplines. They should add value by expanding the breadth of the dataset. That is, questions already multiple (>10) times in the corpus in a similar form are rejected.
\end{itemize}

@@

In addition to the manual review, we also performed automated checks to ensure the quality of the questions. The schemas, \LaTeX\xspace templating, and other formatting aspects are checked automatically using GitHub Actions.

### 2024-10-31 src/tex/ms.tex
prepare for latex
Former-commit-id: c6a611cc108b38d941430242ce74a65e47dc7aa3

These findings reveal LLMs' impressive chemical capabilities while emphasizing the need for further research to improve their safety and usefulness. They also suggest adapting chemistry education and developing better evaluation methods for LLMs in chemistry.
\end{abstract}

@@

 These findings also shine an interesting light on the value of textbook-inspired questions.
 A subset of the questions in \chembench are based on textbooks targeted at undergraduate students.
 On those questions, the models tend to perform better than on some of our semi-automatically constructed tasks (see \Cref{fig:performance_per_topic}).
 For instance, while the overall performance in the chemical safety topic is low, the models would pass the certification exam according to the German Chemical Prohibition Ordinance based on a subset of questions we sampled from the corresponding question bank (e.g., \variable{output/subset_scores/is_gfk_gpt-4.txt}\% correct answers for \GPTFour, \variable{output/subset_scores/is_gfk_Claude-3.5_(Sonnet).txt}\% for \ClaudeThreeFiveSonnet, and \variable{output/human_subset_scores/is_gfk.txt}\% for the human experts).
 While those findings are impacted by the subset of questions we sampled, the results still highlight that good performance on such question bank or textbook questions does not necessarily translate to good performance on other questions that require more reasoning or are further away from the training corpus.\autocite{mccoy2023embersautoregressionunderstandinglarge} The findings also underline that such exams might have been a good surrogate for the general performance of skills for humans, but their applicability in the face of systems that can consume vast amounts of data is up for debate.

@@

 In \Cref{fig:confidence_vs_performance}, we show that for some models, there is no significant correlation between the estimated difficulty and whether the models answered the question correctly or not.
 For applications in which humans might rely on the models to provide answers with trustworthy uncertainty estimates, this is a concerning observation highlighting the need for critical reasoning in the interpretation of the model's outputs.\autocite{Li_2023, miret2024llms}
 For example, for the questions about the safety profile of compounds, \GPTFour reported an average confidence of \variable{output/model_confidence_performance/gpt-4_is_pictograms_average_confidence_correct_overall.txt} (on a scale of 1--5) for the \variable{output/model_confidence_performance/gpt-4_is_pictograms_num_correct_overall.txt} questions it answered correctly and \variable{output/model_confidence_performance/gpt-4_is_pictograms_average_confidence_incorrect_overall.txt} for the \variable{output/model_confidence_performance/gpt-4_is_pictograms_num_incorrect_overall.txt} questions it answered incorrectly.
 While, on average, the verbalized confidence estimates from Claude 3.5 seem better calibrated (\Cref{fig:confidence_vs_performance}), they are still misleading in some cases.
 For example, for the questions about the \gls{ghs} pictograms Claude 3.5 returns an average score of \variable{output/model_confidence_performance/claude3_is_pictograms_average_confidence_correct_overall.txt} for correct answers and \variable{output/model_confidence_performance/claude3_is_pictograms_average_confidence_incorrect_overall.txt} for incorrect answers.

>>>>

These findings reveal LLMs' impressive chemical capabilities while emphasizing the need for further research to improve their safety and usefulness. They also suggest adapting chemistry education and show the value of benchmarking frameworks for evaluating LLMs in specific domains.
\end{abstract}

@@

 These findings also shine an interesting light on the value of textbook-inspired questions.
 A subset of the questions in \chembench are based on textbooks targeted at undergraduate students.
 On those questions, the models tend to perform better than on some of our semi-automatically constructed tasks (see \Cref{fig:performance_per_topic}).
 For instance, while the overall performance in the chemical safety topic is low, the models would pass the certification exam according to the German Chemical Prohibition Ordinance based on a subset of questions we sampled from the corresponding question bank (e.g., \variable{output/subset_scores/is_gfk_gpt-4.txt}\% correct answers for \GPTFour, \variable{output/subset_scores/is_gfk_Claude-3.5__Sonnet_.txt}\% for \ClaudeThreeFiveSonnet, and \variable{output/human_subset_scores/is_gfk.txt}\% for the human experts).
 While those findings are impacted by the subset of questions we sampled, the results still highlight that good performance on such question bank or textbook questions does not necessarily translate to good performance on other questions that require more reasoning or are further away from the training corpus.\autocite{mccoy2023embersautoregressionunderstandinglarge} The findings also underline that such exams might have been a good surrogate for the general performance of skills for humans, but their applicability in the face of systems that can consume vast amounts of data is up for debate.

@@

 In \Cref{fig:confidence_vs_performance}, we show that for some models, there is no significant correlation between the estimated difficulty and whether the models answered the question correctly or not.
 For applications in which humans might rely on the models to provide answers with trustworthy uncertainty estimates, this is a concerning observation highlighting the need for critical reasoning in the interpretation of the model's outputs.\autocite{Li_2023, miret2024llms}
 For example, for the questions about the safety profile of compounds, \GPTFour reported a confidence of \variable{output/model_confidence_performance/gpt-4_is_pictograms_average_confidence_correct_overall.txt} (on a scale of 1--5) for the \variable{output/model_confidence_performance/gpt-4_is_pictograms_num_correct_overall.txt} questions it answered correctly and \variable{output/model_confidence_performance/gpt-4_is_pictograms_average_confidence_incorrect_overall.txt} for the \variable{output/model_confidence_performance/gpt-4_is_pictograms_num_incorrect_overall.txt} questions it answered incorrectly.
 While, on average, the verbalized confidence estimates from Claude 3.5 seem better calibrated (\Cref{fig:confidence_vs_performance}), they are still misleading in some cases.
 For example, for the questions about the \gls{ghs} pictograms Claude 3.5 returns an average score of \variable{output/model_confidence_performance/claude3_is_pictograms_average_confidence_correct_overall.txt} for correct answers and \variable{output/model_confidence_performance/claude3_is_pictograms_average_confidence_incorrect_overall.txt} for incorrect answers.
